---
title: "p8105_hw3_jl6049"
author: "LYU JING"
date: "10/14/2021"
output: github_document
---
## Problem 1


```{r include = FALSE}

library(tidyverse)

```

**1. Load the data from the p8105.datasets**

```{r}
library(p8105.datasets)
data("instacart")
```

**2. Do some exploration of this dataset**

```{r}
instacart =
  instacart %>% 
  janitor::clean_names()

countaisle = count(instacart,aisle)
max_index = filter(countaisle,n == max(countaisle$n))$aisle

```

The dataset contains *`r count(instacart)`* observations of products information from online grocery orders of *`r count(distinct(instacart,user_id))`* distinct Instacart users.

The dataset has 15 columns, including:

**numeric variables:**

* `order_id`
* `product_id`
* `add_to_cart_order`
* `reordered`
* `user_id`
* `order_dow`
* `order_hour_of_day`
* `aisle_id`
* `department_id`
* `order_number`
* `days_since_prior_order`

**character variables:**

* `eval_set`
* `product_name`
* `aisle`
* `department`

Every observation means a certain product in a user's order. The observation contains detail information of the product, the order and the user. 

- For the product information, it has product id, order of each product was added to cart, prodcut has been ordered by this user in the past or not, name of the product, aisle of the product with aisle id and department of the product with department id.
- For the order information, it has order id, evaluation set this order belongs in (train only),the order sequence number for this user, the day of the week on which the order was placed, the hour of the day on which the order was placed and days since the last order.
- For the user information, it has user id.

**3. Answer the following questions**

1)  How many aisles are there, and which aisles are the most items ordered from?

There are **`r count(distinct(instacart,aisle_id))`** aisles.

The most items ordered from **`r filter(countaisle,n == max(countaisle$n))$aisle`** whose frequency is **`r max(countaisle$n)`**.

2)  Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r message=FALSE}
instacart %>%
  count(aisle) %>% 
  filter(n > 10000) %>%
  mutate(
    aisle = fct_reorder(aisle,n)
    ) %>% #reorder/ranking
   mutate(
    stratify = case_when(
      n <=  20000 ~ "under 20000",
      (n > 20000)&(n < 40000) ~ "20000 to 40000",
      n > 40000      ~ "above 40000"
  )) %>% 
  ggplot(aes(x = aisle, y = n, label = n, fill = stratify)) +
  geom_text(check_overlap = TRUE, size = 2, hjust = 0, nudge_x = 0.07) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(
    title = "The Number of Items Ordered in Each Aisle",
    x = "The number of items",
    y = "Aisle",
  )
```


3)  Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r message=FALSE}
most_popular = 
  instacart %>%
  filter(aisle == "baking ingredients" | aisle == "dog food care" | aisle == "packaged vegetables fruits") %>%
  group_by(aisle, product_name) %>% 
  summarize(count = n(),) %>% 
  mutate(order = min_rank(desc(count))) %>% 
  filter(min_rank(desc(count)) < 4) %>% 
  arrange(aisle,order)
  
knitr::kable(most_popular)
```

4)  Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table)

```{r message=FALSE}
meanhour_icecream = 
  instacart %>%
  filter(product_name == "Pink Lady Apples" | product_name == "Coffee Ice Cream") %>%
  
  group_by(product_name,order_dow) %>% 
  summarize(mean_hour = floor(mean(order_hour_of_day)),
            mean_min = 60*(round(mean(order_hour_of_day),1) - floor(mean(order_hour_of_day))),
            mean_time = paste(as.character(mean_hour),as.character(mean_min),sep = ":")
            ) %>% 
  mutate(order_dow = recode(order_dow , 
                            '0' = "Sunday",'1' = "Monday",'2' = "Tuesday",
                            '3' = "Wednesday",'4' = "Thursday",'5' = "Friday",'6' = "Saturday")) %>%
  select(order_dow,mean_time) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_time
  ) 

knitr::kable(meanhour_icecream)
```


## Problem 2

**1. load the data from the p8105.datasets package.**

```{r}
library(p8105.datasets)
data("brfss_smart2010")
BRFSS = brfss_smart2010
```

**2. do some data cleaning**

```{r}
BRFSS = 
  BRFSS %>% 
  # format the data to use appropriate variable names
  janitor::clean_names() %>% 
  # focus on the “Overall Health” topic
  filter(topic == "Overall Health") %>% 
  # to make sure that "response" include only responses from “Excellent” to “Poor”
  # count(response)     
  # organize responses as a factor taking levels ordered from “Poor” to “Excellent”
  mutate(response = factor(response, levels = c("Poor", "Fair", "Good", "Very good", "Excellent"))) 
```

**3. do or answer the following (commenting on the results of each):**

1) In 2002, which states were observed at 7 or more locations? What about in 2010?

*2002:*

```{r}
BRFSS2002 = BRFSS %>%
  filter(year == "2002") %>% 
  count(locationabbr,locationdesc) %>% 
  group_by(locationabbr) %>%
  summarize(n_obs = n()) %>% 
  filter(n_obs >= 7)

knitr::kable(BRFSS2002)

```
*2010:*

```{r message=FALSE}
BRFSS2010 = 
  BRFSS %>%
  filter(year == "2010") %>% 
  count(locationabbr,locationdesc) %>% 
  group_by(locationabbr) %>%
  summarize(n_obs = n()) %>% 
  filter(n_obs >= 7)

knitr::kable(BRFSS2010)
```

2) Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state.

```{r message=FALSE}
BRFSS_exc = 
  BRFSS %>%
  # limited to Excellent responses
  filter(response == "Excellent") %>% 
  group_by(year,locationabbr) %>% 
  # averages the data_value across locations within a state
  summarize(data_value_state_average = mean(data_value, na.rm = TRUE)) 

# Make a “spaghetti” plot of this average value over time within a state  
BRFSS_exc %>% 
  ggplot(aes(x = year, y = data_value_state_average, group = locationabbr)) + 
  geom_line(aes(color = locationabbr)) + 
  theme(legend.position = "right") + 
  labs(
    title = "Spaghetti plot of average data value within a state",
    subtitle = "2002 - 2010",
    y = "average data value within state"
  )
```


3) Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.

```{r message=FALSE}
BRFSS %>%
  filter(locationabbr == "NY") %>% 
  filter(year == "2006" | year == "2010") %>% 
  group_by(year) %>% 
  ggplot(aes(x = response, y = data_value)) + 
  geom_violin(aes(fill = response), alpha = .5) + 
  stat_summary(fun = "median", color = "yellow") +
  coord_flip() +
  facet_grid(~year) +
  labs(
    title = "Distribution of data_value for responses",
    x = "Data_value of locations within NY state",
    y = "Responses"
  )
```

## Problem 3

**1. Load, tidy, and otherwise wrangle the data.**

```{r}
accelerometer_data = read_csv("./accel_data.csv",show_col_types = FALSE)
accelerometer_data =
  accelerometer_data %>% 
  janitor::clean_names() %>% 
  mutate(day_type = ifelse(day == 'Saturday'| day == 'Sunday' ,"weekend" ,"weekday"),
         day_id = recode(day, 
                             "Sunday" = '7', "Monday" = '1',"Tuesday" = '2',
                            "Wednesday" = '3',"Thursday" = '4',"Friday" = '5',"Saturday" ='6')) %>%
  pivot_longer(
    activity_1:activity_1440,
    names_to = "minute",
    names_prefix = "activity_",
    values_to = "value"
  ) %>% 
  mutate(minute = as.numeric(minute)) %>% 
  relocate(day_type) %>% 
  arrange(week,day_id,minute)
  
```
 
 **Describe the resulting dataset (e.g. what variables exist, how many observations, etc).**
 
There are 6 variables. It includes:
day_type : whether the day is a weekday or a weekend
week: the week number
day_id: numbers between 1 to 7, which mean Monday to Sunday accordingly
day: Specific name of Monday to Sunday
minute: the minute when the colletion happened
value: values of accelerometer data

There are 50,400 observations in total.




**Using tidied dataset, aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals.**

```{r message=FALSE}
accelerometer_data_total =
  accelerometer_data %>% 
  group_by(week, day_id, day) %>% 
  summarise(total_activity = sum(value)) %>% 
  arrange(week,day_id) 

knitr::kable(accelerometer_data_total)
```

```{r}
ggplot(accelerometer_data_total, aes(x = day_id, y = total_activity*0.01, color = week)) + 
  geom_line(group = 1) +
  geom_point() +
  scale_x_discrete(
    labels = c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday")) + 
  facet_grid(week~.) +
  knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)


```
From the table, I could tell that activity of Saturday in week 4 and week 5 is 1440, which is impossible for a live person. Maybe in Saturady this person take off the device.

From the plot, I could tell that the general trend in weekdays is quiet similar in week 1,2,5, which is a gradualy increasing trend. But the activity of weekdays are unstable and cannot find out a pattern, especially basing on the incorrect of data collection in Satuardays.

**Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. Describe in words any patterns or conclusions you can make based on this graph.**

```{r}
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)


accelerometer_data %>% 
  ggplot(aes(x = minute, y = value, color = day)) + 
  geom_point(alpha = 1, size = 1) + 
  geom_line(alpha = 0.3) +
  scale_x_continuous(breaks = c(0,120,240,360,480,600,720,840,960,1080,1200,1320,1440),
                     labels = c("0:00","2:00","4:00","6:00","8:00","10:00","12:00","14:00","16:00","18:00","20:00","22:00","24:00")) +
  labs(
    title = "24-hour activity time courses for each day in 5 weeks",
    x = "Minute",
    y = "Value"
  )

```

From the plot we can find out that

From the angle of a day:
We could tell that from 0:00 to 6:00, the person's activity value is very low, which could means that the person's sleep time is in this period. His or her wake-up time is around 6 am. 

From the angle of a week:
at Friday, this person's activity is pretty high from 20:00 to 22:00. He or she may ususally go out and have fun at that time.
at Sunday, this person's activity has a peak from 10:00 to 12:00. He or she may do some routine activities only in Sunday noon.
at Saturday, this person's activity has a small peak from 16:00 to 18:00. He or she may do some routine activities only in Saturday evening.


